### 2014-02-27 paper/concrete.tex
mv local defs to global
moved defs

\Red{Move these definitions earlier}

%{
%format tyerase c = "\varepsilon("c")"
%format tyerasef = "\varepsilon"
%format ^ = " "
%format c = "c"
%format c'
%format cc = "\con{"c"}"
%format cc'
%format ac = "\abs{"c"}"
%format ac'
%format finv = f"^{-1}"
%format V = "V"
%format cV = "\con{"V"}"
%format aV = "\abs{"V"}"
%format ~= = "\approx_l"
%format clequiv = "\con{"~="}"
%format alequiv = "\abs{"~="}"
%format creduce = "\con{".->"}"
%format areduce = "\abs{".->"}"
%format creducestar = "\con{".=>"}"
%format areducestar = "\abs{".=>"}"
%format (ap (f) (x)) = f"("x")"
%format .. = "\circ"
%format idf (t) = "id_{"t"}"

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration, $l$-equivalence and multi-step derivation back.
\end{proof}
%}

>>>>

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration, $l$-equivalence and multi-step derivation back.
\end{proof}

### 2014-02-27 paper/retrofit.tex
Lss
macros
moved defs

\caption{Simple ML-like language}
\label{fig:ml}
\end{figure}

@@

\begin{figure}
\begin{tabular}{ll}
\begin{minipage}{.22\textwidth}
\begin{code}
iv  ::= cdots | IT tv
ie  ::= cdots | IT te
iE  ::= cdots | IT tE
\end{code}
\end{minipage} &
\begin{minipage}{.22\textwidth}
\begin{code}
tv  ::= cdots | TI iv
te  ::= cdots | TI ie
tE  ::= cdots | TI iE
\end{code}
\end{minipage}
\end{tabular}

@@

\begin{mathpar}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}

@@

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{The embedding}
\label{fig:embedding}
\end{figure}

@@

\begin{definition}[Information-flow control language]
    An information-flow control language |L| is a tuple $(|C|, |C|^*, |.->|,
    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
    $|C|^*$ is the type of erased machine configurations, |.->| is a
    reduction relation between machine configurations and $|erasef l|$
    is an erasure function from machine configurations to erased machine
    configurations.  For sequential languages, we may also speak of
    values, e.g. a configurations $V \subseteq |C|$ for which there are
    no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
    if $|erase l c| = |erase l c'|$.
\end{definition}

>>>>

\caption{Simple ML-like language |targetLang ML|}
\label{fig:ml}
\end{figure}

@@

\begin{figure}
%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
%format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
\begin{tabular}{ll}
\begin{minipage}{.22\textwidth}
\begin{code}
iv  ::= cdots | IT tv
ie  ::= cdots | IT te
iE  ::= cdots | IT tE
\end{code}
\end{minipage} &
\begin{minipage}{.22\textwidth}
\begin{code}
tv  ::= cdots | TI iv
te  ::= cdots | TI ie
tE  ::= cdots | TI iE
\end{code}
\end{minipage}
\end{tabular}

@@

\begin{mathpar}
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}

@@

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{The embedding |specLang alpha (targetLang nop)|, where
$|targetLang nop| = (|tS|\times|tE|\times|te|\times|tv|, |->|)$}
\label{fig:embedding}
%}
\end{figure}

@@

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}
